---
title: "Genex Analysis: Fall 2020 pilot 1"
author: "Teresa Gao"
date: "9 October 2020"
output: rmarkdown::github_document
---


# About

This R Notebook reports data from pilot experiments run during Fall 2020 on Proliferate; pilot data was collected for a previous version of this study during Spring 2020 on MTurk. The findings of the latter are occasionally referenced here.



# Setup

Load required libraries

```{r Load libraries}

library("dplyr")
library("tidyverse")
library("ggplot2")
library("gridExtra")
library("tidyboot")

```

If running/editing in RStudio, go to **Session > Set Working Directory > To Source File Location**. This ensures that we can find and access the files we need!

The code below imports the experimental data, as extracted by data_extraction.R

```{r Import data (CSVs)}

system_dava <- read.csv("system_data.csv")
followup_response_data <- read.csv("followup_response_data.csv")
subject_information <- read.csv("subject_information.csv")
trials_data <- read.csv("trials_data.csv") %>% filter(trial_type == "trial")

```



# Calculations and Relabeling

Compute bootstrapped means and confidence intervals of user slider response

```{r Compute boostrapped means, CIs}

CIs <- trials_data %>%
  group_by(item_presentation_condition, n_examples) %>%
  tidyboot_mean(column = response)

```



# Visualization

Box plot of slider response vs. number of examples

```{r Slider response vs. num. examples}

ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = n_examples,
    group = n_examples,
    fill = as.factor(n_examples)
  )
) +
geom_boxplot() +
labs(
  title = "Slider response vs. number of examples",
  x = "Slider response",
  y = "Number of examples"
) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *The plot looks relatively symmetrically distributed. This is not unexpected, since all pilot trials had the same number of examples (1) and are grouped together*
* *As responses for all conditions (accidental and pedagogical) are plotted here, it looks like the responses may have balanced each other out*



Box plot of slider response vs. item presentation condition

```{r Slider response vs. condition}

ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = item_presentation_condition,
    group = item_presentation_condition,
    fill = as.factor(item_presentation_condition)
  )
) +
geom_boxplot() +
labs(
  title = "Slider response vs. item presentation condtion",
  x = "Slider response",
  y = "Item presentation condition"
) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *Accidental condition slider response appears to have greater variability; this is consistent with previous pilot trials of this condition*
* *Pedagogical condition slider response median value is greater than Q3 for accidental (!)*



Box plot of average slider response time for each subject, grouped by number of examples

```{r Avg. slider response time vs. num. examples}

ggplot(
  trials_data,
  mapping = aes(
    x = response_time_in_seconds,
    y = n_examples,
    group = n_examples,
    fill = as.factor(n_examples)
  )
) +
geom_boxplot() +
labs(
  title = "Average slider response time",
  x = "Average time (sec)",
  y = "Number of examples"
) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *For 1 example: Median response time is around 10 seconds (about double the median for Spring 2020 pilots on MTurk), with several large outliers*



Box plot of average slider response time for each subject, grouped by item presentation condition

```{r Avg. slider response time vs. condition}

ggplot(
  trials_data,
  mapping = aes(
    x = response_time_in_seconds,
    y = item_presentation_condition,
    group = item_presentation_condition,
    fill = as.factor(item_presentation_condition)
  )
) +
geom_boxplot() +
labs(
  title = "Average slider response time",
  x = "Average time (sec)",
  y = "Item presentation condition") +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *Accidental condition participants had median slider response time greater than Q3 for pedagogical; perhaps this, along with the wider slider response distribution, reflect greater participant uncertainty?*
* *Accidental condition also saw two high outliers*



Facet grid of slider response plotted on number of examples vs. item presentation condition

```{r Slider response on num. examples vs. condition}

ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..],
    fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16
) +
labs(
  x = "Slider response", y = "Fraction of total count"
) +
facet_grid(n_examples ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *Both accidental and pedagogical distributions saw wide spread*
* *Low accidental peak < 0.5; high pedagogical peak at 1.0*



Facet grid of slider response plotted on number of examples vs. item presentation condition and item property

```{r Slider response on num examples vs. condition and property}

ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..], fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16
) +
labs(
  x = "Slider response",
  y = "Fraction of total count"
) +
facet_grid(property + n_examples ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *Accidental condition: squeaking is grouped in mid-high range; purple petals are in mid-low; accidental green feathers is lowest overall*
* *Pedagogical condition: purple petals grouped in middle to mid-high range; squeaking spread widely from < 0.5 to 1.0*
* *Unclear if squeaking presentation is causing strange range of slider responses; will revisit this trend with greater sample size*



Facet grid of slider response plotted on speaker vs. item presentation condition

```{r Slider response on speaker vs. condition}

ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..],
    fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16) +
labs(
  x = "Slider response",
  y = "Fraction of total count"
) +
facet_grid(speaker ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *Some conditions (accidental/sb, pedagogical/tg) with relatively high spread*
* *As with other facet grids above, later larger sample size should confirm or refute these observed patterns*



Line range of slider response means and confidence intervals grouped by item presentation condition

```{r Slider response means and CIs vs. condition}

ggplot() +
geom_linerange(
  CIs,
  mapping = aes(
    x = item_presentation_condition,
    ymin = ci_lower,
    ymax = ci_upper,
    color = as.factor(item_presentation_condition)),
  size = 1
) +
geom_point(
  CIs,
  mapping = aes(
    x = item_presentation_condition,
    y = mean),
  alpha = 0.5,
  size = 2
) +
scale_color_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
labs(
  y = "Slider response",
  x = "Item presentation condition"
) +
theme(legend.position = "none")

```

*Observations:*

* *Both pedagogical and accidental appear to have similar confidence intervals; this was also true for Spring 2020 pilot data*
* *Mean pedagogical slider response is about 0.15 higher than mean accidental slider response, which is close to the 0.10 from the spring*



Gradient density ridges graph of slider response vs. item presentation condition

```{r Gradient plot of slider response vs. condition}
ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = item_presentation_condition, fill = ..x..
  )
) +
  ggridges::geom_density_ridges_gradient(
    jittered_points = T, alpha = 0.8, scale = 0.95,
    position = ggridges::position_points_jitter(width = 0.01, height = 0),
    point_shape = "|", point_size = 2.5, point_alpha = 0.3,
    rel_min_height = 0.01, gradient_lwd = 1,
    stat = "binline", bins = 25, draw_baseline = F
  ) +
  ggstance::geom_linerangeh(
    CIs,
    inherit.aes = F,
    mapping = aes(
      xmin = ci_lower, xmax = ci_upper,
      y = as.numeric(item_presentation_condition) + 0.8
    ),
    size = 1.25, color = "black"
  ) + geom_point(
    CIs,
    inherit.aes = F,
    mapping = aes(
      x = mean,
      y = as.numeric(item_presentation_condition) + 0.8
    ),
    size = 3, color = "black", shape = 3
  ) +
  scale_x_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1.02),
    breaks = c(0, 0.25, 0.5, 0.75, 1)
  ) +
  scale_y_discrete(expand = c(0.01, 0)) +
  viridis::scale_fill_viridis(
    name = "Implied Prevalence", option = "D",
    breaks = c(0, 1)
  ) +
  guides(fill = F) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_text(hjust = 0.5, vjust = 0)
  ) +
  labs(x = "Probability of Future Instance having Property")

```
