---
title: "Genex Analysis: Fall 2020 Prolific pilots"
author: "Teresa Gao"
date: "17 November 2020"
output: rmarkdown::github_document
---


# About

This R Notebook reports data from a second ("third") round of pilot experiments run during Fall 2020 on Prolific (via proliferate).



# Setup

Load required libraries

```{r libraries}

library("dplyr")
library("tidyverse")
library("ggplot2")
library("gridExtra")
library("tidyboot")
library("ngram")
library("readr")
library("tidytext")
library("stringr")
library("readr")
library("brms")

```

If running/editing in RStudio, go to **Session > Set Working Directory > To Source File Location**. This ensures that we can find and access the files we need!

```{r import and filter data}

streamlined_data <- read_csv("../../../prolific/2020-fall/pilot-3/genex-pilot-3-streamlined_data.csv")
n_total_participants <- nrow(streamlined_data)

# remove participants who failed attention and/or followup
streamlined_data <- streamlined_data %>%
  # filter(catch_trial_fails == 0) %>%
  filter(followup_fails == 0)

View(streamlined_data) # prints output; line may be omitted

```

Due to failure of attention checks and/or non-comprehension followup questions, `r n_total_participants - nrow(data)` participants were excluded from analysis.



# Calculations and Relabeling

Compute bootstrapped means and confidence intervals of user slider response

```{r means and CIs}

predicted_probability_CIs <- streamlined_data %>%
  group_by(item_presentation_condition, n_examples) %>%
  tidyboot_mean(column = predicted_probability)

predicted_probability_duration_CIs <- streamlined_data %>%
  group_by(item_presentation_condition, n_examples) %>%
  tidyboot_mean(column = predicted_probability_duration)

generic_endorsement_CIs <- streamlined_data %>%
  group_by(item_presentation_condition, n_examples) %>%
  mutate(generic_endorsement = ifelse(generic_endorsement == "yes",1,0)) %>%
  tidyboot_mean(column = generic_endorsement)
generic_endorsement_CIs # prints output; line may be omitted

perceived_character_knowledge_CIs <- streamlined_data %>%
  group_by(item_presentation_condition, n_examples) %>%
  mutate(perceived_character_knowledge = ifelse(perceived_character_knowledge == "yes",1,0)) %>%
  tidyboot_mean(column = perceived_character_knowledge)
perceived_character_knowledge_CIs # prints output; line may be omitted

```



# Visualization

## Predicted probability

Gradient density ridges graph of predicted probability of next encountered object having same property vs. item presentation condition and number of examples

```{r gradient density - predicted probability vs. condition}

predicted_probability_CIs <- predicted_probability_CIs %>%
    mutate(exp_cond = factor(paste(item_presentation_condition, n_examples, sep = "_")))

ggplot(
  streamlined_data %>%
      mutate(exp_cond = paste(item_presentation_condition, n_examples, sep = "_")),
  mapping = aes(
    x = predicted_probability,
    y = exp_cond,
    fill = ..x..
  )
) +
  ggridges::geom_density_ridges_gradient(
    jittered_points = T, alpha = 0.8, scale = 0.95,
    position = ggridges::position_points_jitter(width = 0.01, height = 0),
    point_shape = "|", point_size = 2.5, point_alpha = 0.3,
    rel_min_height = 0.01, gradient_lwd = 1,
    stat = "binline", bins = 25, draw_baseline = F
  ) +
  ggstance::geom_linerangeh(
    predicted_probability_CIs,
    inherit.aes = F,
    mapping = aes(
      xmin = ci_lower, xmax = ci_upper,
      y = as.numeric(exp_cond) + 0.85
    ),
    size = 1.25, color = "black"
  ) + geom_point(
    predicted_probability_CIs,
    inherit.aes = F,
    mapping = aes(
      x = mean,
      y = as.numeric(exp_cond) + 0.85
    ),
    size = 3, color = "black", shape = 3
  ) +
  scale_x_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1.02),
    breaks = c(0, 0.25, 0.5, 0.75, 1)
  ) +
  scale_y_discrete(expand = c(0.01, 0)) +
  viridis::scale_fill_viridis(
    breaks = c(0, 1)
  ) +
  guides(fill = F) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_text(hjust = 0.5, vjust = 0)
  ) +
  labs(x = "Predicted Probability of Future Instance having Property")
```

Gradient density ridges graph of *time taken to respond* to predicted probability of next encountered object having same property vs. item presentation condition and number of examples

```{r gradient density - predicted probability time vs. condition}

predicted_probability_duration_CIs <- predicted_probability_duration_CIs %>%
    mutate(exp_cond = factor(paste(item_presentation_condition, n_examples, sep = "_")))

ggplot(
  streamlined_data %>%
      mutate(exp_cond = paste(item_presentation_condition, n_examples, sep = "_")),
  mapping = aes(
    x = predicted_probability_duration,
    y = exp_cond,
    fill = ..x..
  )
) +
  ggridges::geom_density_ridges_gradient(
    jittered_points = T, alpha = 0.8, scale = 0.95,
    position = ggridges::position_points_jitter(width = 0.01, height = 0),
    point_shape = "|", point_size = 2.5, point_alpha = 0.3,
    rel_min_height = 0.01, gradient_lwd = 1,
    stat = "binline", bins = 25, draw_baseline = F
  ) +
  ggstance::geom_linerangeh(
    predicted_probability_duration_CIs,
    inherit.aes = F,
    mapping = aes(
      xmin = ci_lower, xmax = ci_upper,
      y = as.numeric(exp_cond) + 0.85
    ),
    size = 1.25, color = "black"
  ) + geom_point(
    predicted_probability_duration_CIs,
    inherit.aes = F,
    mapping = aes(
      x = mean,
      y = as.numeric(exp_cond) + 0.85
    ),
    size = 3, color = "black", shape = 3
  ) +
  scale_x_continuous(
    expand = c(0.01, 0),
    breaks = c(0, 0.25, 0.5, 0.75, 1)
  ) +
  scale_y_discrete(expand = c(0.01, 0)) +
  viridis::scale_fill_viridis(
    breaks = c(0, 1)
  ) +
  guides(fill = F) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_text(hjust = 0.5, vjust = 0)
  ) +
  labs(x = "Response time for predicted probability of future instance having property")
```

Facet grid of predicted probability plotted on number of examples vs. item presentation condition

```{r facet grid - predicted probability on num. examples vs. condition}
ggplot(
  streamlined_data,
  mapping = aes(
    x = predicted_probability,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..],
    fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16
) +
labs(
  x = "Slider response",
  y = "Fraction of total count"
) +
facet_grid(n_examples ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")
```

Facet grid of predicted probability plotted on item presentation condition vs. speaker

```{r facet grid - predicted probabiliy on condition vs. speaker}
ggplot(
  streamlined_data,
  mapping = aes(
    x = predicted_probability,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..],
    fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16) +
labs(
  x = "Slider response",
  y = "Fraction of total count"
) +
facet_grid(speaker ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")
```

## Followup

<!-- TODO -->