---
title: "Genex Analysis: Fall 2020 Prolific pilots"
author: "Teresa Gao"
date: "16 October 2020"
output: rmarkdown::github_document
---


# About

This R Notebook reports data from pilot experiments run during Fall 2020 on Prolific (via proliferate); pilot data was collected for a previous version of this study during Spring 2020 on MTurk (via nosub). The findings of the latter are occasionally referenced here.



# Setup

Load required libraries

```{r Load libraries}

library("dplyr")
library("tidyverse")
library("ggplot2")
library("gridExtra")
library("tidyboot")
library("ngram")
library("readr")
library("tidytext")
library("stringr")
library("readr")
library("brms")

```

If running/editing in RStudio, go to **Session > Set Working Directory > To Source File Location**. This ensures that we can find and access the files we need!

The code below imports the experimental data, as extracted by data_extraction.R; this removes data from participants who failed attention checks before or after main experiment.

Make sure to run data_extraction.R before continuing!

```{r Import data (CSVs)}
system_data <- read_csv("system_data.csv")
catch_data <- read_csv("catch_data.csv")
followup_data <- read_csv("followup_data.csv")
subject_information <- read_csv("subject_information.csv")
trials_data <- read_csv("trials_data.csv") %>% filter(trial_type == "trial")

```



# Calculations and Relabeling



Add word- and character-count columns as new freeform followup response data data frame

```{r Create freeform followup df with word- and char-count}

freeform_followup <- followup_data %>% filter(response_type == "freeform")

freeform_followup <- freeform_followup %>%
  mutate(n_words = str_count(response, pattern=boundary(type="word"))) %>%
  mutate(n_chars = str_count(response, pattern=boundary(type="character")))

```



Compute bootstrapped means and confidence intervals of user slider response

```{r Compute boostrapped means and CIs}

predicted_probability_CIs <- trials_data %>%
  group_by(item_presentation_condition, n_examples) %>%
  tidyboot_mean(column = response)

slider_response_time_CIs <- trials_data %>%
  group_by(item_presentation_condition, n_examples) %>%
  tidyboot_mean(column = response_time_in_seconds)

generic_endorsement_CIs <- followup_data %>%
  filter(response_type == "slider") %>%
  group_by(proliferate.condition) %>%
  type.convert() %>% # `chr` to `dbl`
  tidyboot_mean(column = response, na.rm=TRUE)

generic_endorsement_CIs

trials_data %>%
  group_by(item_presentation_condition, n_examples)

freeform_followup_wordcount_CIs <- freeform_followup %>%
  group_by(proliferate.condition) %>%
  tidyboot_mean(column = n_words, na.rm=TRUE)

```


Create data frame comparing slider responses in-trial vs. in-followup

```{r Create df to compare trial/generic endorsements}

predicted_probabilitys <- trials_data %>%
  select(workerid, response, response_time, item_presentation_condition, n_examples) %>%
  rename(
    predicted_probability = response,
    predicted_probability_time = response_time
  )

generic_endorsements <- followup_data %>%
  filter(response_type == "slider") %>%
  select(workerid, response, response_time) %>%
  rename(
    generic_endorsement = response,
    generic_endorsement_time = response_time
  )

all_sliders <- inner_join(predicted_probabilitys, generic_endorsements, by="workerid") %>%
  mutate(generic_endorsement = as.double(generic_endorsement)) %>%
  mutate(trials_minus_generic_endorsements = predicted_probability - generic_endorsement)

```



# Visualization

## Trials data

Gradient density ridges graph of slider response vs. item presentation condition

```{r Gradient plot of slider response vs. condition}

predicted_probability_CIs <- predicted_probability_CIs %>%
    mutate(exp_cond = factor(paste(item_presentation_condition, n_examples, sep = "_")))
ggplot(
  trials_data %>%
    mutate(exp_cond = paste(item_presentation_condition, n_examples, sep = "_")),
  mapping = aes(
    x = response,
    y = exp_cond, 
    fill = ..x..
  )
) +
  ggridges::geom_density_ridges_gradient(
    jittered_points = T, alpha = 0.8, scale = 0.95,
    position = ggridges::position_points_jitter(width = 0.01, height = 0),
    point_shape = "|", point_size = 2.5, point_alpha = 0.3,
    rel_min_height = 0.01, gradient_lwd = 1,
    stat = "binline", bins = 25, draw_baseline = F
  ) +
  ggstance::geom_linerangeh(
    predicted_probability_CIs,
    inherit.aes = F,
    mapping = aes(
      xmin = ci_lower, xmax = ci_upper,
      y = as.numeric(exp_cond) + 0.8
    ),
    size = 1.25, color = "black"
  ) + geom_point(
    predicted_probability_CIs,
    inherit.aes = F,
    mapping = aes(
      x = mean,
      y = as.numeric(exp_cond) + 0.8
    ),
    size = 3, color = "black", shape = 3
  ) +
  scale_x_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1.02),
    breaks = c(0, 0.25, 0.5, 0.75, 1)
  ) +
  scale_y_discrete(expand = c(0.01, 0)) +
  viridis::scale_fill_viridis(
    breaks = c(0, 1)
  ) +
  guides(fill = F) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_text(hjust = 0.5, vjust = 0)
  ) +
  labs(x = "Probability of Future Instance having Property")

```



Gradient density ridges graph of slider response *time* vs. item presentation condition

```{r Gradient plot of slider response time vs. condition}

slider_response_time_CIs <- slider_response_time_CIs %>%
    mutate(exp_cond = factor(paste(item_presentation_condition, n_examples, sep = "_")))
ggplot(
  trials_data %>%
    mutate(exp_cond = paste(item_presentation_condition, n_examples, sep = "_")),
  mapping = aes(
    x = response_time,
    y = exp_cond, 
    fill = ..x..
  )
) +
  ggridges::geom_density_ridges_gradient(
    jittered_points = T, alpha = 0.8, scale = 0.95,
    position = ggridges::position_points_jitter(width = 0.01, height = 0),
    point_shape = "|", point_size = 2.5, point_alpha = 0.3,
    rel_min_height = 0.01, gradient_lwd = 1,
    stat = "binline", bins = 25, draw_baseline = F
  ) +
  ggstance::geom_linerangeh(
    slider_response_time_CIs,
    inherit.aes = F,
    mapping = aes(
      xmin = ci_lower, xmax = ci_upper,
      y = as.numeric(exp_cond) + 0.8
    ),
    size = 1.25, color = "black"
  ) + geom_point(
    slider_response_time_CIs,
    inherit.aes = F,
    mapping = aes(
      x = mean,
      y = as.numeric(exp_cond) + 0.8
    ),
    size = 3, color = "black", shape = 3
  ) +
  scale_x_continuous(
    expand = c(0.01, 0),
    limits = c(0, max(trials_data$response_time)*1.1)
  ) +
  scale_y_discrete(expand = c(0.01, 0)) +
  viridis::scale_fill_viridis(
    breaks = c(0, 1)
  ) +
  guides(fill = F) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_text(hjust = 0.5, vjust = 0)
  ) +
  labs(x = "Slider response time in seconds")

```



Facet grid of slider response plotted on number of examples vs. item presentation condition

```{r Slider response on num. examples vs. condition}

ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..],
    fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16
) +
labs(
  x = "Slider response",
  y = "Fraction of total count"
) +
facet_grid(n_examples ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *Wide spread in all conditions and example counts*
* *Pedagogical mode at 1.0 for both 1 and 2 examples*
* *1-example accidental mode below 0.5; 2-example accidental distributed mostly above 0.5*
* *Naive similarly distributed as accidental for both 1 and 2 examples*



Facet grid of slider response plotted on number of examples vs. item presentation condition and item property

```{r Slider response on num examples vs. condition and property}

ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..], fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16
) +
labs(
  x = "Slider response",
  y = "Fraction of total count"
) +
facet_grid(property + n_examples ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *Accidental condition: 2-example purple petals and 2-example squeaking are high-clustered; 1-example green feathers is low-clustered*
* *Pedagogical condition: 2-example purple petals seem to have weakest inference strength*



Facet grid of slider response plotted on speaker vs. item presentation condition

```{r Slider response on speaker vs. condition}

ggplot(
  trials_data,
  mapping = aes(
    x = response,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..],
    fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16) +
labs(
  x = "Slider response",
  y = "Fraction of total count"
) +
facet_grid(speaker ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```

*Observations:*

* *High mode of 1.0 for sb/pedagogical*



## Attention check and followup response data



Scatter plot of each condition's trials slider response to generic endorsement response

```{r Conditions' slider responses vs. generic endorsement responses}

# TODO

```



Scatter plot of all trials slider responses to generic endorsement response

```{r All trials' slider responses vs. generic endorsement response}

ggplot(
  all_sliders,
  mapping = aes(
    x = predicted_probability,
    y = generic_endorsement,
    color = item_presentation_condition
  )
) +
  labs(
    title = "Trials slider response vs. generic endorsement response",
    x = "Trials slider response",
    y = "generic endorsement response"
  ) +
  geom_point() +
  scale_color_manual(
    values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
  )

```

*Observations*

* *Does not seem to be clear 1:1 relationship between slider responses nor even strong linear relationship*
* *Suggests participants may perceive difference between inferring event (e.g., witnessing another example with same feature) vs. inferring generic (e.g., "All Xs do Y")*



Facet grid of difference between trial and generic endorsement responses plotted on number of examples vs. item presentation condition

```{r Slider diff. on num. examples vs. item presentation condition}

ggplot(
  all_sliders,
  mapping = aes(
    x = trials_minus_generic_endorsements,
    y = (..count..) / tapply(..count.., ..PANEL.., sum)[..PANEL..],
    fill = as.factor(item_presentation_condition)
  )
) +
geom_histogram(
  color = "black",
  bins = 16) +
labs(
  x = "Trials slider response - generic endorsement response",
  y = "Fraction of total count"
) +
facet_grid(n_examples ~ item_presentation_condition) +
scale_fill_manual(
  values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
) +
theme(legend.position = "none")

```



Scatter plot of freeform followup word count vs. difference between trial and generic endorsement responses

```{r Followup wordcount vs. slider diff.}

ggplot(
  merge(all_sliders, freeform_followup),
  mapping = aes(
    x = n_words,
    y = trials_minus_generic_endorsements,
    color = item_presentation_condition
  )
) +
  labs(
    title = "Freeform followup word count vs. trials generic endorsement response diff",
    x = "Num words in freeform followup",
    y = "Trials slider response - generic endorsement response"
  ) +
  geom_point() +
  scale_color_manual(
    values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
  )

```



Scatter plot of generic endorsement response word count vs. character count

```{r Freeform followup word vs. char count}

ggplot(
  merge(freeform_followup, trials_data[, c("workerid", "item_presentation_condition")], by="workerid"),
  mapping = aes(
    x = n_words,
    y = n_chars,
    color = item_presentation_condition
  )
) +
  labs(
    title = "Freeform followup word vs. character count",
    x = "Number of words in freeform followup",
    y = "Number of characters in freeform followup"
  ) +
  geom_point() +
  scale_color_manual(
    values = c("indianred1", "lightgoldenrod1", "darkolivegreen2", "cornflowerblue")
  )

```

*Observations*

* *Relationship appears linear, even with high outliers*



Plot of word frequency for top 10 in freeform followup responses for each condition

```{r Freeform followup word frequency}

freeform_followup_frequency <- freeform_followup %>%
  unnest_tokens(word, response) %>%
  anti_join(stop_words) %>%
  group_by(proliferate.condition, word) %>%
  summarise(frequency=n())

ggplot(freeform_followup_frequency %>% top_n(10), aes(word, frequency)) +
  geom_col(aes(fill=proliferate.condition)) +
  xlab(NULL) +
  scale_y_continuous(expand = c(0,0)) +
  coord_flip() +
  labs(fill = "Condition", title="Freeform followup word frequency for top 10 words") +
  scale_fill_brewer() +
  scale_fill_manual(
    values = c("indianred1", "indianred2", "lightgoldenrod1", "lightgoldenrod2", "darkolivegreen2", "darkolivegreen3", "cornflowerblue", "dodgerblue3")
  )

```